04_DESeq_sexes

### 2019-08-28 analysis/04_DESeq2_sexes.Rmd
now with LDA 9 group and 3 groups

  mydata <- left_join(tvsd, mycolData, by = "V1")  # merge counts and variables
  mydata$V1 <- NULL

@@

>>>>

  mydata <- left_join(tvsd, mycolData, by = "V1")  # merge counts and variables
  mydata$V1 <- NULL
  mydata$sextissue <- NULL

@@

```{r LDA2}

LDAanalysis2 <- function(mydds, mycolData, mysubtitle){
  # data prep
  vsd <- vst(mydds, blind=FALSE) # variance stabilized 
  tvsd <- as.data.frame(t(assay(vsd)))   # get vsd counts and transform

  mydata <- left_join(tvsd, mycolData, by = "V1")  # merge counts and variables
  mydata$V1 <- NULL
  mydata$sextissue <- NULL
  mydata$hypothesis <- NULL

  # LDA analysis
  # Fit the model
  model <- lda(treatment~ ., data = train.transformed)
  # Make predictions
  predictions <- model %>% predict(test.transformed)
  # Model accuracy
  mean(predictions$class==test.transformed$treatment)

  # LDA plot using ggplot2 
  lda.data <- cbind(train.transformed, predict(model)$x)
  p <- ggplot(data = lda.data, aes(LD1, LD2, color = treatment, shape = sex)) +
    geom_point() +
    labs(subtitle = mysubtitle)
  plot(p)

LDAanalysis2(dds.hypothalamus, colDataHyp, "Hypothalamus")
LDAanalysis2(dds.pituitary, colDataPit, "Pituitary")
LDAanalysis2(dds.gonad, colDataGon, "Gonad")

```
